Rugsafe: A Multichain Vault Protocol for Recovering from \& Defending Against Rug Pulls

### 2024-10-03 rugsafe_original_old_merged/rugsafe/paper/paper.tex
updated folder structure with broken out contracts
updated paper

\title{Rugsafe: A Multichain Vault Protocol for Defending Against Rug Pulls}
\author{info@rugsafe.org}
\date{v0.0.1 September 1, 2024}

@@

\begin{abstract}
Rugsafe introduces a comprehensive protocol aimed at mitigating the risks of rug pulls in the cryptocurrency ecosystem. By utilizing cryptographic security measures and economic incentives, the protocol provides a secure multichain system for recovering assets and transforming rugged tokens into opportunities and rewards. Foundational to Rugsafe are specialized vaults where rugged tokens can be securely deposited, and anticoin tokens are issued as receipts. Users can utilize these anticoins within the ecosystem or choose to burn them, further securing the protocol and earning additional rewards. The supply of the native Rugsafe token is dynamically adjusted based on the volume, value, and activity of rugged tokens, ensuring stability and resilience. By depositing rugged tokens into a vault on several chains, and by burning anticoins, users receive incentives on the RugSafe chain. This protocol's vaults are designed to work in heterogenous blockchain ecosystems, offering a practical and effective solution to one of the most significant challenges in the cryptocurrency market. 
\end{abstract}

@@

The Rugsafe protocol enables users who hold rugged tokens, denoted as $C_r$, to deposit these tokens into a specialized vault $V_c$ and receive anticoin tokens, $C_a$,  which serve as receipts, \(\mathcal{R} \). The supply of Rugsafe's native token, $R$, is regulated based on the total value of rugged tokens in existence.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Vault Creation and Anticoin Issuance}
When a vault $V_c$ is created for a rugged token $C_r$, users can deposit $C_r$ into this vault. Upon deposit, the protocol mints an equal amount of $C_a$ tokens, which are credited to the user's balance. These $C_a$ tokens serve as a new, clean fungible token for the rugged victim, issued 1:1 with the underlying rugged token.

@@

In addition to the 1:1 $C_a$ tokens, the user may also receive a receipt, \(\mathcal{R} \) , in the form of a non-fungible token (NFT) or a refungible token (RFT). The 1:1 $C_a$ token acts as a standard fungible token, fully transferable and tradable. However, the receipt could also be issued as an NFT, representing a unique claim on the deposited rugged tokens. Alternatively, the receipt can be an RFT, where an NFT representing the deposit is held by a contract. The contract then distributes shares of the NFT by issuing a fungible token that serves as representative shares of the underlying NFT.

@@

where $\text{type}$ determines whether the receipt is a fungible token, an NFT, or an RFT. This provides flexibility depending on the specific use case or preferences of the depositor. The vaults are held in a central vault registry, ensuring that all interactions with rugged tokens are tracked and managed within the system. Regardless of the type of receipt issued, depositors always receive the 1:1 $C_a$ tokens as a clean representation of their original rugged tokens.

\subsection{Withdrawal Penalty Mechanism}
If a user decides to withdraw their original rugged tokens $C_r$ by depositing back their $C_a$, a penalty is incurred. A portion of the $C_a$ tokens are deducted from the user's balance, and these penalized tokens are distributed among the remaining $C_a$ holders.

\begin{equation}
C_{r,w} = C_{r,d} - P(C_a)
\end{equation}

Where $P(C_a)$ represents the penalty, which scales according to the amount of $C_r$ originally deposited, \(d\). The penalty mechanism incentivizes holding $C_a$ longer, as the remaining holders benefit from these penalties.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

where emission rate, $R_\epsilon$, is a parameter that determines the number of Rugsafe tokens emitted per block.

@@

\subsection{Anticoin Role and Market Interaction}
At the time of vault creation, the protocol mints $C_a$ tokens in a 1:1 ratio with the deposited rugged tokens $C_r$. These $C_a$ tokens serve as a clean, fungible representation of the rugged tokens, providing users with a new asset that can be freely traded or held. The value of $C_a$ tokens is determined entirely by market forces, \(m_f\), allowing the broader ecosystem to establish their worth relative to other assets.

The $C_a$ tokens function purely as receipts for the deposited rugged tokens and do not undergo any price adjustments or pegging mechanisms. This approach ensures that the protocol remains simple and transparent, with the market dictating the value of $C_a$ based on supply and demand dynamics.

@@

>>>>

\title{Rugsafe: A Multichain Vault Protocol for Recovering from \& Defending Against Rug Pulls}
\author{info@rugsafe.org}
\date{v0.0.1 September 1, 2024}

@@

\begin{abstract}
Rugsafe introduces a comprehensive protocol aimed at mitigating the risks of rug pulls in the cryptocurrency ecosystem. By utilizing cryptographic security measures and economic incentives, the protocol provides a secure multichain system for recovering assets and transforming rugged tokens into opportunities and rewards. Foundational to Rugsafe are specialized vaults where rugged tokens can be securely deposited, and anticoin tokens are issued as receipts. These anticoins are designed to be inversely pegged to the price movement of the underlying rugged token. Users can utilize these anticoins within the ecosystem or choose to burn them, further securing the protocol and earning additional rewards. The supply of the native Rugsafe token is dynamically adjusted based on the volume, value, and activity of rugged tokens, ensuring stability and resilience. By depositing rugged tokens into a vault on several chains, and by burning anticoins, users receive incentives on the RugSafe chain. This protocol's vaults are designed to work in heterogenous blockchain ecosystems, offering a practical and effective solution to one of the most significant challenges in the cryptocurrency market. 
\end{abstract}

@@

The Rugsafe protocol enables users who hold rugged tokens, denoted as $C_r$, to deposit these tokens into a specialized vault $V_c$ and receive anticoin tokens, $C_a$,  which serve as receipts, \(\mathcal{R} \), and are inversely pegged to the value of the underlying rugged token. The supply of Rugsafe's native token, $R$, is regulated based on the total value of rugged tokens in existence.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ANTICOINS

\subsection{Vault Creation and Anticoin Issuance}
When a vault $V_c$ is created for a rugged token $C_r$, users can deposit $C_r$ into this vault. Upon deposit, the protocol mints an equal amount of $C_a$ tokens, which are credited to the user's balance. These $C_a$ tokens serve as a new, clean fungible token for the rugged victim, issued 1:1 with the underlying rugged token and are inversely pegged to its value.

@@

In addition to the 1:1 $C_a$ tokens, the user may also receive a receipt, \(\mathcal{R} \), in the form of a non-fungible token (NFT) or a refungible token (RFT). The 1:1 $C_a$ token acts as a standard fungible token, fully transferable and tradable. However, the receipt could also be issued as an NFT, representing a unique claim on the deposited rugged tokens. Alternatively, the receipt can be an RFT, where an NFT representing the deposit is held by a contract. The contract then distributes shares of the NFT by issuing a fungible token that serves as representative shares of the underlying NFT.

@@

where $\tau$ determines whether the receipt is a fungible token, an NFT, or an RFT. This provides flexibility depending on the underlying asset type. The vaults are held in a central vault registry per blockchain ecosystem, and ultimately represented on the Rugsafe blockchain, ensuring that all interactions with rugged tokens are tracked and managed within the multichain ecosystem. Regardless of the type of receipt issued, depositors always receive the 1:1 $C_a$ tokens as a clean representation of their original rugged tokens.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ANTICOIN ROLE

\subsection{Anticoin Role and Market Interaction}

At the time of vault creation, the protocol mints $C_a$ tokens in a 1:1 ratio with the deposited rugged tokens $C_r$. These $C_a$ tokens serve not only as receipts for the deposited tokens but also as inversely, logarithmically pegged assets. This inverse logarithmic peg allows users to benefit from a decline in the value of $C_r$, effectively creating a hedge against further depreciation of rugged tokens.

\begin{figure}[h]
\centering
\includegraphics[width=\textwidth]{images/anticoins.png}
\caption{The plotted relationship between the price of a rugged token ($C_r$) and the price of its anticoin ($C_a$) under an inverse logarithmic model. In the left plot, as $C_r$ increases linearly, the price of $C_a$ decreases logarithmically, demonstrating a diminishing response in $C_a$ as $C_r$ grows. In the right plot, as $C_r$ decreases, the price of $C_a$ rises logarithmically, tapering off as $C_r$ approaches zero. This inverse peg mechanism ensures that $C_a$ responds proportionally to changes in $C_r$, maintaining stability and mitigating volatility.}
\label{fig:anticoins_plot}
\end{figure}

Unlike traditional stablecoins, the value of $C_a$ tokens increases as the value of $C_r$ decreases, following an inverse, logarithmic price relationship. This dynamic creates a unique market interaction where $C_a$ holders are incentivized to retain their tokens when the value of $C_r$ declines.

The inverse logarithmic peg mechanism, as depicted in Figure \ref{fig:anticoins_plot}, ensures that $C_a$ tokens adjust logarithmically based on the real-time market movements of the underlying $C_r$. Unlike bounded inverse assets, the $C_a$ tokens are not constrained by any upper or lower price limits, allowing for unrestricted value increases as $C_r$ approaches zero.

This design ensures that $C_a$ tokens serve dual purposes within the protocol. They serve as a receipt for deposited rugged tokens and as an inversely, logarithmically pegged asset that can be freely traded or held. The valuation of $C_a$ is driven by market forces, allowing the broader ecosystem to determine its worth relative to other assets based on supply, demand, and the inverse relationship with the rugged token $C_r$.

%%%%%%%%%% bounding
\subsubsection{Inverse Logarithmic Pegging as Soft Theoretical Bounds}

Linear inverse pegs in previous systems required artificial bounds on asset prices. Once these bounds were reached, the asset froze, and a new version was created. These restrictions were designed to prevent extreme price volatility but imposed artificial constraints that limited flexibility and created friction through asset freezes, and resets.

In contrast, the inverse logarithmic peg for $C_a$ naturally establishes soft theoretical bounds without requiring such freezes. As the price of $C_r$ moves to either extreme, the logarithmic peg ensures the price of $C_a$ tapers off, maintaining stability. This tapering effect acts as a soft boundary, ensuring proportional price responses without hard limits or resets.

\[
C_{a}(t) = \log\left(\frac{C_{r}(0)}{C_{r}(t)}\right)
\]

Where \( C_{a}(t) \) is the value of the anticoin at time \( t \), \( C_{r}(0) \) is the rugged token's price at vault creation, and \( C_{r}(t) \) is its real-time price. This relationship ensures that all $C_a$ holders share a uniform reference point.

This approach provides more organic price regulation, allowing the market to drive $C_a$’s value while avoiding the volatility issues seen in bounded systems. The logarithmic peg offers a flexible, stable framework that adapts naturally to market conditions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%% SUPPLY

@@

where $\text{emission\_rate}$ is a parameter that determines the number of Rugsafe tokens emitted per block.

@@

@@

% things to add
% perpetuals market
% asymmetric funding rates
% anticoins inverse price with dex
% defi suite
% prediction market
% borroing and lending
